Translocation notebook

### 2022-03-06 doc/notebook/notebook_translocation.Rmd
Change notebook format to html_document

---
title: "Notebook"
author: "Roland Knapp"
date: "`r Sys.Date()`"
output:
  html_notebook
---

```{r message=FALSE}
library(tidyverse)
```

@@

```{r frog-lenth-weight-plot, echo=FALSE}
read_csv(here::here("data", "clean", "frog_translocation.csv")) %>% 
ggplot(aes(x = log10(length), y = log10(weight))) +
  geom_point() +
  geom_smooth(method = "lm")
plot
```

>>>>

---
title: "Translocation notebook"
author: "Roland Knapp"
date: "`r Sys.Date()`"
output:
  html_document
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, results='hide')
```

```{r}
library(tidyverse)
```

@@

```{r frog-length-weight-plot}
read_csv(here::here("data", "clean", "frog_translocation.csv")) %>% 
ggplot(aes(x = log10(length), y = log10(weight))) +
  geom_point() +
  geom_smooth(method = "lm")
plot
```
